=enter title here=

### 2021-08-26 paper/agujournaltemplate.tex
Results part of paper

We stacked the 8th level detail of the wavelet decomposition of the displacement over all the GPS stations located in a 50 km radius of a given point, for the 16 locations indicated in Figure 3. The result is shown in the top panel of Figure 6, where each line represents one of the locations. To better highlight the peaks in the wavelet details, we highlighted in red the time intervals where the amplitude of the stacked detail is higher than a threshold, and in blue the  time intervals where the amplitude of the stacked detail is lower than minus the threshold. To compare the GPS signal with the tremor signal, we plotted the 8th level detail of the wavelet decomposition of the tremor count on the bottom panel of Figure 6. We used the opposite of the cumulative tremor count for the wavelet decomposition in order to be able to match positive peaks with positive peaks and negative peaks with negative peaks.

@@

>>>>

We stacked the 8th level detail of the wavelet decomposition of the displacement over all the GPS stations located in a 50 km radius of a given point, for the 16 locations indicated in Figure 3. The result is shown in the top panel of Figure 6, where each line represents one of the locations. To better highlight the peaks in the wavelet details, we highlighted in red the time intervals where the amplitude of the stacked detail is higher than a threshold, and in blue the  time intervals where the amplitude of the stacked detail is lower than minus the threshold. To compare the GPS signal with the tremor signal, we plotted the 8th level detail of the wavelet decomposition of the tremor count on the bottom panel of Figure 6. We used the opposite of the cumulative tremor count for the wavelet decomposition in order to be able to match positive peaks with positive peaks and negative peaks with negative peaks. Although the latitudinal extension of the events is not always the same for the GPS data and for the tremor data, we identify the same 10 events in both 8th wavelet decompositions for the 8th level: Summer 2010, Summer 2011, Summer 2012, Fall 2013, Summer-Fall 2014, Winter 2015-2016, Winter 2017, Spring 2018, Spring-Fall 2019, and Fall 2020 - Winter 2021. We can also see the end of an 11th event in Summer 2009. \\

@@

Figures 7 and 8 show the same comparison between the wavelet decomposition of the GPS data and the wavelet decomposition of the tremor count data for the 7th level and the 6th level respectively. For the 7th level, we see the same events as for the 8th level, both for the GPS data and the tremor count data. The wavelet decomposition is more noisy for the GPS data in the earliest part of the time series, between 2010 and 2013, but it does not seem that there are more slow slip events visible in the 7th level. \\

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/GPS_detail_7.pdf}

\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/tremor_detail_7.pdf}
\caption{Top: Stacked 7th level details of the wavelet decomposition of the displacement over all the GPS stations located in a 50 km radius of a given point, for the 16 locations indicated in Figure 3. Bottom: Opposite of the 7th level detail of the cumulative tremor count in a 50 km radius of a given point for the same 16 locations.}
\label{pngfiguresample}
\end{figure}

For the 6th level detail, we see an additional event in Fall 2009 that is present both in the GPS and the tremor data. There are three small signals in the GPS data in Spring 2012, Fall 2017, and Winter 2020 that are not present in the tremor data, and are probably false detections. To summarize, all the 11 events present on the 7th and 8th level details of the wavelet decomposition are true detections, 12 of the 15 events present on the 6th level detail of the wavelet decomposition are true detections.

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/GPS_detail_6.pdf}

\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/tremor_detail_6.pdf}
\caption{Top: Stacked 6th level details of the wavelet decomposition of the displacement over all the GPS stations located in a 50 km radius of a given point, for the 16 locations indicated in Figure 3. Bottom: Opposite of the 6th level detail of the cumulative tremor count in a 50 km radius of a given point for the same 16 locations.}
\label{pngfiguresample}
\end{figure}
